Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-10-13 Manuscript.Rmd
updated bib (use _orig but add new sources)

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
- \usepackage{fixltx2e}
- \pagestyle{myheadings}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
    fig_caption: yes
csl: apa.csl
indent: true
bibliography: bibliography.bib
geometry: margin=1in
---

<!-- NOTES: 
- If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
- This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
- Numbers on each chunk correspond generally to sections in the preregistrations (https://osf.io/2rsgm/registrations)
- Within the Setups chunk, the 'figsEnd' variable dictates whether figs are shown at the end (T) or intermixed in the text (F)
-->

>>>>

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
- \usepackage{fixltx2e}
- \pagestyle{myheadings}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
    fig_caption: yes
  word_document: default
csl: apa.csl
indent: yes
bibliography: bibliography.bib
geometry: margin=1in
---

<!-- NOTES AND TIPS: 
- If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
- This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
- Numbers on each chunk correspond generally to sections in the preregistrations (https://osf.io/2rsgm/registrations)
- Within the Setups chunk, the 'figsEnd' variable dictates whether figs are shown at the end (T) or intermixed in the text (F)
-->
